---
title: ""
output: word_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```


```{r}
library(tidyverse)
library(flextable)
library(ftExtra)
library(officer)
library(here)

```



```{r}

cr_timing_in_table <- function(zmod_tab) {
mod_table <- zmod_tab %>% 
  data.frame() %>% 
  mutate(Neg2LnL = -2 * LL) %>% 
  select(model.structure, K, Delta_AICc, AICcWt, Neg2LnL) %>% 
  mutate(across(.cols = c(Delta_AICc, AICcWt, Neg2LnL),  ~format(round(., 2), nsmall = 2)))
return(mod_table)
}

#
fix_cr_age_mod_names <- function(zmod.table) {
  zmod.table <- zmod.table %>% 
  mutate(Modnames = gsub("\\.", " * ", Modnames),
         Modnames = gsub("_", " + ", Modnames),
         Modnames = gsub("sex", "Sex", Modnames),
         Modnames = gsub("year", "Yr", Modnames),
         Modnames = gsub("hatch", "Hatch", Modnames),
         Modnames = gsub("mass", "Mass", Modnames),
         Modnames = gsub("tib", "Tibio", Modnames),
         Modnames = gsub("flip", "Flipper", Modnames),
         Modnames = gsub("int", "Intercept only", Modnames)
         )
  return(zmod.table)
}




cr_timing_out_table <- function(step1_mod_tab, step2_mod_tab) {
  step1bestaic <- step1_mod_tab %>% 
    filter(Delta_AICc == 0) %>% 
    select(AICc) %>% 
    mutate(AICc = round(AICc, 2))
  step2bestaic <- step2_mod_tab %>% 
    filter(Delta_AICc == 0) %>% 
    select(AICc) %>% 
    mutate(AICc = round(AICc, 2))
out_table <- rbind(
  # step 1
  data.frame(model.structure = paste("Step 1.\nbest model AICc =", step1bestaic$AICc), K = "", Delta_AICc = "", AICcWt = "", Neg2LnL = ""),
  step1_mod_tab %>% cr_timing_in_table(),
  # step 2
  data.frame(model.structure = paste("Step 2.\nbest model AICc =", step2bestaic$AICc), K = "", Delta_AICc = "", AICcWt = "", Neg2LnL = ""),
  step2_mod_tab %>% cr_timing_in_table())

flextable(out_table) %>% 
    set_header_labels(model.structure = "Model structure",
                    Delta_AICc = "\u0394 AICc",
                    AICcWt = "AICc wt",
                    Neg2LnL = "-2lnL") %>% 
  align(j = 2:5, align = "center", part = "all") %>% 
  border(i = 1, j = 1, border.bottom = fp_border(color = "black"), part = "body") %>% # step 1 sub border
  border(i = 1 + nrow(step1_mod_tab), border.bottom = fp_border(color = "black"), part = "body") %>% # step 2 top border
  border(i = 2 + nrow(step1_mod_tab), j = 1, border.bottom = fp_border(color = "black"), part = "body") %>% # step 2 sub border
  autofit() %>% 
  colformat_md() %>% 
  width(j = 1, width = 3.5) %>% 
  width(j = 2, width = .5) %>% 
  width(j = 3:5, width = 1)
}


multitable_survival <- function(p_tab, phi_tab, p_phi_tab) {
  p_modtable <- p_tab %>% 
  rename(model.structure = p.stru) %>% 
  mutate(across(c(QAICc, DeltaQAICc, weight, QDeviance), ~round(., 3)))

p_best_aic <- p_modtable %>% 
  filter(DeltaQAICc == 0) %>% 
  select(QAICc)


phi_modtable <- phi_tab %>%
  rename(model.structure = phi.stru) %>%  
  mutate(across(c(QAICc, DeltaQAICc, weight, QDeviance), ~round(., 3)))

phi_best_aic <- phi_modtable %>% 
  filter(DeltaQAICc == 0) %>% 
  select(QAICc)

p_phi_modtable <- p_phi_tab %>% 
  mutate(across(c(QAICc, DeltaQAICc, weight, QDeviance), ~round(., 3)))

p_phi_best_aic <- p_phi_modtable %>% 
  filter(DeltaQAICc == 0) %>% 
  select(QAICc)


rbind(data.frame(model.structure = paste("A. Determining p structure\nbest model QAICc = ", p_best_aic$QAICc, sep = ""), npar = "", DeltaQAICc = "", weight = "", QDeviance = ""),
      p_modtable %>% 
  select(model.structure, npar, DeltaQAICc, weight, QDeviance),
      data.frame(model.structure = paste("B. Determining \u03D5 structure\nbest model QAICc = ", phi_best_aic$QAICc, sep = ""), npar = "", DeltaQAICc = "", weight = "", QDeviance = ""),
      phi_modtable %>% 
  select(model.structure, npar, DeltaQAICc, weight, QDeviance),
      data.frame(model.structure = paste("C. Best \u03D5 and p structure from above (\u0394 QAICc < 5)\nbest model QAICc = ", p_phi_best_aic$QAICc, sep = ""), npar = "", DeltaQAICc = "", weight = "", QDeviance = ""),
      p_phi_modtable %>% 
  select(model.structure, npar, DeltaQAICc, weight, QDeviance)) %>%
  flextable() %>% 
  set_header_labels(model.structure = "Model structure",
                    npar = "K",
                    DeltaQAICc = "\u0394 QAICc",
                    weight = "QAICc wt") %>% 
  align(j = 2:5, align = "center", part = "all") %>% 
  border(i = 1, j = 1, border.bottom = fp_border(color = "black"), part = "body") %>% 
  border(i = nrow(p_modtable) + 1, border.bottom = fp_border(color = "black"), part = "body")%>% 
  border(i = 1 + nrow(p_modtable) + 1, j = 1, border.bottom = fp_border(color = "black"), part = "body") %>% 
  border(i = nrow(p_modtable) + 1 + nrow(phi_modtable) + 1, border.bottom = fp_border(color = "black"), part = "body") %>% 
  border(i = 1 + nrow(p_modtable) + 1 + nrow(phi_modtable) + 1, j = 1, border.bottom = fp_border(color = "black"), part = "body") %>% 
  autofit() %>% 
  colformat_md() %>%
  width(j = 1, width = 3.5) %>% 
  width(j = 2, width = .5) %>% 
  width(j = 3:5, width = 1)
}





singletable_phi <- function(phi_tab) {
  phi_modtable <- phi_tab %>%
  rename(model.structure = phi.stru) %>%  
  mutate(across(c(QAICc, DeltaQAICc, weight, QDeviance), ~round(., 3)))

phi_best_aic <- phi_modtable %>% 
  filter(DeltaQAICc == 0) %>% 
  select(QAICc)

phi_modtable %>% 
  select(model.structure, npar, DeltaQAICc, weight, QDeviance) %>% 
  flextable() %>% 
  set_header_labels(model.structure = paste("\u03D5 model structure\nbest model QAICc = ", phi_best_aic$QAICc, sep = ""),
                    npar = "K",
                    DeltaQAICc = "\u0394 QAICc",
                    weight = "QAICc wt") %>% 
  align(j = 2:5, align = "center", part = "all") %>% 
  autofit() %>% 
  colformat_md() %>% 
  width(j = 1, width = 3.5) %>% 
  width(j = 2, width = .5) %>% 
  width(j = 3:5, width = 1)
}




```


Model selection tables for linear and Cormack-Jolly-Seber (CJS) models used in Trade-offs in offspring-rearing behavior: understanding the relationships between growth, brood-guarding, and offspring survival in the Adélie Penguin

In all tables, shown for each model are the model structure, the number of parameters (K), the difference between model Akaike Information Criterion adjusted for small sample sizes (AICc; linear models) or small sample sizes and overdispersion (QAICc; CJS models) and the lowest AICc/QAICc in the model set (ΔAICc/ΔQAICc), Akaike weights (AICc wt/QAICc wt), and either -2 * loglikelihood (-2lnL) for linear models or Quasi deviance (QDeviance) for CJS models. Multi-part tables represent multi-step model selection processes: we first determined the best supported structure among the variables not directly related to our questions. We then took all models from the first step with ΔAICc/ΔQAICc < 5 and no uninformative parameters (uninformative parameters indicated with `r knitr::asis_output(sprintf("^\u2020^"))`, parentheses and `r knitr::asis_output(sprintf("^\u2020^"))` around interactions indicates the interaction term was uninformative) and added structure to represent the variables directly related to our hypotheses. The intercept-only model was included in early steps for comparison.



Table S1. Model selection results for the linear models we used to evaluate the potential factors associated with the age that Adélie Penguin chicks entered the crèche stage at Cape Crozier, Ross Island, Antarctica, 2012-2013. Step 1 variables considered were years (Yr), males vs. females (Sex), and relative chick hatch date (Hatch). Step 2 variables were growth rate in mass (g; Mass), flipper length (mm; Flipper), and tibiotarsus length (mm; Tibio).  

```{r}

cr_timing_out_table(
 readRDS(here("fitted_models/cr_timing/cr_age_step1_mods"))$model.table,
  readRDS(here("fitted_models/cr_timing/cr_age_step2_mods"))$model.table
)




```


Table S2. Model selection results for the linear models we used to evaluate the potential factors associated with flipper length when Adélie Penguin chicks entered the crèche stage at Cape Crozier, Ross Island, Antarctica, 2012-2013. Step 1 variables considered were years (Yr), males vs. females (Sex), and relative chick hatch date (Hatch). Step 2 variables were Crèching age and growth rate in flipper length (mm; Flipper).

```{r}
cr_timing_out_table(
  readRDS(here("fitted_models/cr_timing/cr_flip_step1_mods"))$model.table,
  readRDS(here("fitted_models/cr_timing/cr_flip_step2_mods"))$model.table
)



```

Table S3. Model selection results for the linear models we used to evaluate the potential factors associated with tibiotarsus length when Adélie Penguin chicks entered the crèche stage at Cape Crozier, Ross Island, Antarctica, 2012-2013. Step 1 variables considered were years (Yr), males vs. females (Sex), and relative chick hatch date (Hatch). Step 2 variables were Crèching age and growth rate in Tibiotarsus length (mm; Tibio).
```{r}
cr_timing_out_table(
  readRDS(here("fitted_models/cr_timing/cr_tib_step1_mods"))$model.table,
readRDS(here("fitted_models/cr_timing/cr_tib_step2_mods"))$model.table
)



```

Table S4. Model selection results for the linear models we used to evaluate the potential factors associated with mass when Adélie Penguin chicks entered the crèche stage at Cape Crozier, Ross Island, Antarctica, 2012-2013. Step 1 variables considered were years (Yr), males vs. females (Sex), and relative chick hatch date (Hatch). Step 2 variables considered were Crèching age and growth rate in flipper length (g: Mass).
```{r}
cr_timing_out_table(
  readRDS(here("fitted_models/cr_timing/cr_mass_step1_mods"))$model.table,
  readRDS(here("fitted_models/cr_timing/cr_mass_step2_mods"))$model.table
)
```


Table S5. Model selection results from Cormack-Jolly-Seber models to estimate underlying resighting (p) and survival probabilities (`r knitr::asis_output("\u03D5")`) of Adélie Penguin chicks during the entire chick-provisioning period at Cape Crozier, Ross Island, Antarctica, 2012-2013. Variables considered were year (Yr), sex, relative hatch date (Hatch), crèche status (brood/guard stage vs. crèched; Crèche), and within season temporal variation including general variation (t), linear (T), pseudo-threshold (lnT) and quadratic (TT) patterns. 


```{r}

multitable_survival(readRDS(here("fitted_models/survival/step1.1_p"))$model.table,
                    readRDS(here("fitted_models/survival/step1.2_phi"))$model.table,
                    readRDS(here("fitted_models/survival/step1.4"))$model.table)
```
<br>


Table S6. Model selection results from Cormack-Jolly-Seber models to estimate the effect of chick age and brood vs. guard status on survival probabilities (`r knitr::asis_output("\u03D5")`) of Adélie Penguin chicks across the entire chick-provisioning period at Cape Crozier, Ross Island, Antarctica, 2012-2013. In this stage of model selection we used all model structures with `r knitr::asis_output("\u0394 QAICc")` < 5 from Table S5C as the starting point, and added two time-varying variables to the `r knitr::asis_output("\u03D5")` structure which were directly related to our research questions: chick age on each day (Age) and chick crèche status on each day (brood/guard stage vs. crèched; Crèche). 



```{r}

singletable_phi(readRDS(here("fitted_models/survival/step2"))$model.table)

```


<br>

Table S7.  Model selection results from Cormack-Jolly-Seber models to estimate underlying patterns of resighting probability and survival of Adélie Penguin chicks during the crèche period at Cape Crozier, Ross Island, Antarctica, 2012-2013. In this stage of model selection we fitted models only to those chicks that reached the crèche stage (n = 84). We considered most of the same model structures as we considered in Table S5 above, except that we excluded crèche status.

```{r}
multitable_survival(readRDS(here("fitted_models/survival/step5.1_creched_p"))$model.table, 
                    readRDS(here("fitted_models/survival/step5.2_creched_phi"))$model.table,
                    readRDS(here("fitted_models/survival/step5.4_creched_base"))$model.table)

```

<br>

Table S8. Model selection results for estimating the effects of crèching age and size on survival probabilities of Adélie Penguin chicks during the crèche period at Cape Crozier, Ross Island, Antarctica, 2012-2013. Models in this candidate set were built from the model structures with `r knitr::asis_output("\u0394")` QAICc < 5 from Table S7C, plus variables representing the age (Cr age), mass (g; Cr mass), flipper length (mm; Cr flipper), and tibiotarsus length (mm; Cr tibio) when each chick entered the crèche stage. 

```{r}
singletable_phi(readRDS(here("fitted_models/survival/step6_cr_timing_surv"))$model.table)
```
